Collective behavior of Janus Particles Suspended in a Viscous Fluid

### 2022-08-03 doc/PRF2022/PRF_main.tex
yny

% \affiliation command applies to all authors since the last
% \affiliation command. The \affiliation command should follow the
% other information
% \affiliation can be followed by \email, \homepage, \thanks as well.
\author{Szu-Pei Fu}
\email{peter.fu@trincoll.edu}
\affiliation{Department of Mathematics, Trinity College, Hartford, Connecticut 06106, USA}

%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\author{Rolf Ryham}
\email{rryham@fordham.edu}
\affiliation{Department of Mathematics, Fordham University, Bronx, New York 10458, USA}

\author{Bryan Quaife}
\email{bquaife@fsu.edu}
 \affiliation{Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA}
 \author{Y.-N. Young}
 \email{yyoung@njit.edu}
 \affiliation{Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, New Jersey 07102, USA
 }

>>>>

% \affiliation command applies to all authors since the last
% \affiliation command. The \affiliation command should follow the
% other information
% \affiliation can be followed by \email, \homepage, \thanks as well.
\author{Szu-Pei Fu$^{1}$, Rolf Ryham$^{2}$, Bryan Quaife$^{3}$ and Y.-N. Young$^{4}$}
%\email{peter.fu@trincoll.edu}
\affiliation{$^1$Department of Mathematics, Trinity College, Hartford, Connecticut 06106, USA\\
$^2$Department of Mathematics, Fordham University, Bronx, New York 10458, USA \\
$^3$Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA\\
$^4$Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, New Jersey 07102, USA}

%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
%\author{Rolf Ryham}
%\email{rryham@fordham.edu}
%\affiliation{Department of Mathematics, Fordham University, Bronx, New York 10458, USA}
%
%\author{Bryan Quaife}
%\email{bquaife@fsu.edu}
 %\affiliation{Department of Scientific Computing, Florida State University, Tallahassee, Florida 32306, USA}
 %\author{Y.-N. Young}
 %\email{yyoung@njit.edu}
 %\affiliation{Department of Mathematical Sciences, New Jersey Institute of Technology, Newark, New Jersey 07102, USA}
